A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-18 paper/main.tex

\title{A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
%\titlenote{whatever titlenote here}

@@

\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
\todo[inline]{The abstract should come now}
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and it's audio-only variant (i.e. audio-description), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}). The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), and \aPhonesAll\ phonemes.

Zusätzliche Annos der Worte

This annotation enables further studies of language perception and semantic processing under conditions of real-life complexity using the studyforrest dataset.

@@

% hier sind “sentences” nicht vollständige Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
% Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am
% Ende gekennzeichnet.
For this publication, we annotated the onsets and offsets, and content of sentences, single words and phonemes spoken in the audio-visual (AV) movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its corresponding audio-only (AO) variant (i.e. audio-description) for visually impaired persons \citep{ForrestGumpDVD}.
% paper regarding mention musical not mentioned
fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
Additional fMRI data include retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.

@@

\subsection*{Annotation procedure}
\todo[inline]{wo kommen die "preliminaries transcriptions" etc.? Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{speech-vocal.csv}}
Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv}), non-speech vocalizations (e.g. laughing or groaning; \texttt{non\_speech\_vocalization.json}), and the audio-description's narrator
(\texttt{german\_audio\_description.csv}) were merged (\texttt{speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{speech-vocal.TextGrid}).
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing one onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
The following steps were done in several passes to iteratively improve the quality of the data:
Approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
\todo[inline]{what is a regular audience? without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat ;-)}
When two or more persons were speaking simultaneously the less dominant voice was dropped.
Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by the audience were dropped, too.

% Alignment preparations
We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences.
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes within every word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of single phonemes. To improve the quality of the automatic alignment, this dictionary was manually updated with German words that were missing in the dictionary but occur in the stimuli. The pronunciation of English words occurring in the otherwise German audio track was taken from an English pronunciation dictionary provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.

% Alignment
\todo[inline]{Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach). kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
The audio file was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
This WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment.
In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected in Praat, again interatively in several passes.
Onsets and offsets of words and their corresponding phonemes on which the automatic alignment performed moderately were corrected.
Some (low volume) sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s. table \ref{tab:overview} for an overview of the annotation's content).
In a third step, the name of the speaker was added for every sentence (cf. table \ref{tab:speakers} for the most often occurring speakers).
During every new step results from previous steps were checked again for errors and corrected.

\begin{table*}[tbp]
\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments used during fMRI scanning. The label ``Sentences''' comprises complete grammatical sentences (i.e. having a subject and a predicate) or questions that are additionally marked with a full stop or question mark.
The  label ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g. ``ha, ha, ha'') or in isolation (e.g. ``ha'', at time points when speakers rapidly switch). The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[btp]
\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie. Shown names are mostly identical to the names used in \citep{labs2015portrayed}. Overall 97 persons were identified.}
\label{tab:speakers}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% NLP
To automatically analyze linguistic features of words in their corresponding
sentence, we employed the Python package spaCy v2.2.1
(\href{https://spacy.io}{spacy.io}) and a German language model
(de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de})
trained on the TIGER Treebank corpus
(\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}). We performed
analyses regarding part of speech (i.e. grammatical tagging or word-category
disambiguation), syntactic dependency, lemmatization, word embedding (i.e.
semantic similarity), and if the word is one of the most common words of the
German language. Results of these analyzes were added to the annotation and
saved as .TextGrid file. This .TextGrid file was converted via python script to
a tab separated file in accordance with the brain imaging data structure
(\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
% BIDS stuff runter zu "Dataset content"?

\subsection*{Data Legend}
% wo wurde automatisch korrigiert (e.g. NE/NN, NONSPEECH)
% s. dictionaries oben in add_part-of-speech-tagging2textgrid.py

@@

% einige Eigennamen (NE/NN) wurden automatisch korrigiert, weil das Sprachmodell
% die naheliegenderweise nicht kannte; eine Liste dieser Eigennamen befindet
% sich oben in dem entsprechendem Skript
% (add_part-of-speech-tagging2textgrid.py)
\subsubsection*{Simple part-of-speech tag (\texttt{pos})}
This column contains tags for whole sentences ("SENTENCE"), phonemes ("PHONEME") and non-speech vocalizations (NONSPEECH). For single words, it contains a simple part-of-speech tagging (grammatical tagging; word-category disambiguation) taking the relationship with adjacent and related words in the same sentence into account (s. table \ref{tab:pos}). This simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.

\begin{table*}[t]
\caption{Simple part of speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
\label{tab:pos}
\begin{tabular}{lllllllllll}
\toprule
\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

% discussion
% careful what you pretend, check & cite (again)
% \citep{binder2009semantic, dewitt2012phoneme}.
Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
All contrasts show bilateral clusters in speech-related regions (e.g. ) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}

\section*{Data availability}
% aus der Schnitt-Annotation übernommen
\texttt{This section will be auto-generated.}

>>>>

\title{A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description}
%\titlenote{whatever titlenote here}

@@

\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and it's audio-only variant (i.e. audio-description), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}). The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
For every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a semantic analysis in terms of word embedding (word2vector). This annotation enables further studies of language perception and semantic processing under conditions of real-life complexity using the studyforrest dataset.

@@

\todo[inline]{``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh"); Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am Ende gekennzeichnet. In der Tabelle ist es aber ausführlich beschrieben}
For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual (AV) movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its corresponding audio-only (AO) variant (i.e. audio-description) for visually impaired persons \citep{ForrestGumpDVD}.
fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
Additional fMRI data include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.

@@

\subsection*{Annotation procedure}
\todo[inline]{wo kommen die "preliminaries transcriptions" etc.? Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{speech-vocal.csv}}
Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv}), non-speech vocalizations (e.g. laughing or groaning; \texttt{non\_speech\_vocalization.json}), and the audio-description's narrator
(\texttt{german\_audio\_description.csv}) were merged (\texttt{speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{speech-vocal.TextGrid}).
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing one onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
The following steps were done in several passes to iteratively improve the quality of the data:
Approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
When two or more persons were speaking simultaneously the less dominant voice was dropped.
Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by the audience were dropped, too.
\todo[inline]{what is a regular audience? without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat}

% Alignment preparations
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences.
To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
To improve the detection rate of the automatic alignment, this dictionary was manually updated with German words that occur in the stimuli but were missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
The pronunciation of English words and phonemes occurring in the otherwise German audio track was taken from an English pronunciation dictionary (following the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

% Alignment
\todo[inline]{Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach). kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
The audio file was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
This WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment.
In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes on which the automatic alignment performed moderately were corrected in Praat interatively in several passes.
Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s. table \ref{tab:overview} for an overview of the annotation's content regarding sentences, words, and phonemes).
In a third step, the name of the speaker was added for every sentence (cf. table \ref{tab:speakers} for the most often occurring speakers).
During every new step results from previous steps were checked again for errors.

\begin{table*}[tbp]
\caption{Overview of the speech annotation's content for the whole stimulus and its individual segments used during fMRI scanning. The label ``Sentences'' comprises complete grammatical sentences (i.e. comprising subject predicate) which are additionally marked with a full stop at the end.
The label ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g. ``ha, ha, ha'') or in isolation (e.g. ``ha'' at time points when speakers switch rapidly). The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[btp]
\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie. Names are mostly identical to the names used in \citep{labs2015portrayed}. Overall 97 persons were identified.}
\label{tab:speakers}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% NLP
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
To automatically analyze linguistic features of words in their corresponding
sentence, we employed the Python package spaCy v2.2.1
(\href{https://spacy.io}{spacy.io}) and its accompanying German language model
(\texttt{de\_core\_news\_md} trained on the TIGER Treebank corpus \citep{brants2004tiger}.
Non-speech vocalizations were dropped from the sentences before analysis.
We then performed analyses regarding part-of-speech (i.e. grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e. semantic similarity), and if the word is one of the most common words of the German language.
Results of these analyzes were added to the annotation which is available as a Praat TextGrid file (\texttt{fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a tab separated file (\texttt{fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).

\subsection*{Data Legend}

@@

% einige Eigennamen (NE/NN) wurden automatisch korrigiert, weil das Sprachmodell
% die naheliegenderweise nicht kannte; eine Liste dieser Eigennamen befindet
% sich oben in dem entsprechendem Skript
% add_part-of-speech-tagging2textgrid.py
\subsubsection*{Simple part-of-speech tag (\texttt{pos})}
This column contains tags for whole sentences ("SENTENCE"), phonemes ("PHONEME") and non-speech vocalizations (NONSPEECH). For single words, it contains a simple part-of-speech tagging (grammatical tagging; word-category disambiguation) taking the relationship with adjacent and related words in the same sentence into account (s. table \ref{tab:pos}). This simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.

\begin{table*}[t]
\caption{Simple part-of-speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
\label{tab:pos}
\begin{tabular}{lllllllllll}
\toprule
\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

% discussion
% careful what you pretend, check & cite (again)
% \citep{binder2009semantic, dewitt2012phoneme}.
Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
All contrasts show bilateral clusters in speech-related regions (e.g. ) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}
\section*{Data availability}
% aus der Schnitt-Annotation übernommen
\texttt{This section will be auto-generated.}
